Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-18 README.Rmd
updated to do list

- Edit dataset descriptions in README and add to the readme.txt document for submission
- Go through all steps in the sumbission steps (one more time)
- Upload the files for submission and submit

>>>>

- Edit dataset descriptions in README and add to the readme.txt document for submission
- Upload the files for submission and submit
